Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-04-11 article.rnw
Refactor the rnw file to get num_species and num_obs from the InputData object.
Add an `is_per_capita` variable to the InputData object.

	input_data <- InputData$new("output/focal-vector.data", "output/response-vector.data", "output/design-matrix.data")

	num_species <- nrow(species_dat)
	num_obs <- nrow(read.table("output/design-matrix.data"))

>>>>

	input_data <- InputData$new("output/focal-vector.data", "output/response-vector.data", "output/design-matrix.data", is_per_capita=TRUE)

	num_species <- input_data$num_species
	num_obs <- input_data$num_obs
